Survival Analysis

### 2014-05-02 paper.Rnw
Copy-paste-modify section for accel. fail. time model.

We can view the $\mathbf{x' \beta}$ factor in the model above as a modifier for the time-to-event $T$ that streatches and shrinks the survival rate horizontally.

>>>>

We can view the $\mathbf{x' \beta}$ factor in the model above as a modifier for the time-to-event $T$ that streatches and shrinks the survival rate horizontally. In expanded form, this linear term would look like $x_1 \beta_1 + x_2 \beta_2 + x_3 \beta_3 + \ldots$ which would simplify to $\exp(x_1 \beta_1) \exp(x_2 \beta_2) \exp(x_3 \beta_3) \ldots$ when we exponentiate both sides, ignoring the error term. In this form, we can see that the scaling factors are not additive, but multiplicative. If an $x\beta$ were to be 0, the resulting scaling factor would be $\exp(0) = 1$ which is the same as saying ``this factor has no effect on the time-to-event.''
